Table on stock change factors per clinate zone

### 2021-04-01 ResultNotebooks/results_SOCflows.Rmd
add revision point by point replies

LivstCropLoss     <- CropFEED - ManureExcretedTot - LivstCropHANPP 
CropPRIMLoss      <- CropPRIM + ResPRIM + LivstCropHANPP # assume verything gets re-emitted at the end

>>>>

LivstCropLoss     <- CropFEED + ResFEED - ManureExcretedTot - LivstCropHANPP 
CropPRIMLoss      <- CropPRIM + ResPRIM + LivstCropHANPP # assume verything gets re-emitted at the end

### 2021-04-01 ResultNotebooks/results_SOCmaps.Rmd
add revision point by point replies

rev <- "rev16"

@@

scenarios    <- c("histManagement","constManagement-1975", "constTillage-mixedtill", "constResidues-1975", "constManure-1975",
                  "constManagement2-1975", "constResrate-1975", "constYield-1975",
                 "Initial-natveg", "Initial-natveg_constManangement-1975", "Initial-natveg_constManangement2-1975", 
                 "LitterPNV-PerennialGrasses", "LitterPNV-AASS", "LitterPNV-BRCF", 
                 "LitterPNV-MTCF", "LitterPNV-BLEAF",  "LitterPNV-TREF")

# for(item in scenarios){
#    dir.create(path=paste0("Data/",paste0(rev,item)))
#    untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
#    files=filesNeeded, exdir=paste0("Data/", paste0(rev,item)), extras="--keep-newer-files ")
# }

@@

SoilCarbon <- read.magpie(paste0("Data/histManagement/SoilCarbon.rds"))
Landuse    <- read.magpie(paste0("Data/histManagement/Landuse.rds"))

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission)[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC'))) +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(trans = squish_trans(-18,0,10),
                     limits = c(-28,0),
                     breaks = c(0, -20, -22, -24, -26, -28)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 10, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size)#,
        #plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
        ) +
  annotate(geom="text", label="SOC debt", x=factor(1995), y=-20, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -24, arrow=arrow(end="both", type="closed", length=unit(0.1, "inches")))

@@

grid <- plot_grid(SOCdensity,SOCincrease, SOCshare, SOCemis,  ncol=2, labels=c("(a)","(b)", "(c)", "(d)"),
                  label_fontface = "plain", label_size = 10)
grid
ggsave(paste0(outputdir,"/4panelfigure.png"), plot=grid, width = 20, height = 14, dpi = 300, units = "cm")

>>>>

rev <- "rev19"
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")

@@

scenarios    <- c("histManagement")#,"constManagement-1975", "constTillage-mixedtill", "constResidues-1975", "constManure-1975",
                  #"constManagement2-1975", "constResrate-1975", "constYield-1975",
                 #"Initial-natveg", "Initial-natveg_constManangement-1975", "Initial-natveg_constManangement2-1975", 
                 #"LitterPNV-PerennialGrasses", "LitterPNV-AASS", "LitterPNV-BRCF", 
                 #"LitterPNV-MTCF", "LitterPNV-BLEAF",  "LitterPNV-TREF")

for(item in scenarios){
   dir.create(path=paste0("Data/",paste0(rev,item)))
   untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
   files=filesNeeded, exdir=paste0("Data/", paste0(rev,item)), extras="--keep-newer-files ")
}

@@

SoilCarbon <- read.magpie(paste0("Data/",rev,scenarios[1],"/SoilCarbon.rds"))
Landuse    <- read.magpie(paste0("Data/",rev,scenarios[1],"/Landuse.rds"))

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission)[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC'))) +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(trans = squish_trans(-42,0,10),
                     limits = c(-46,0),
                     breaks = c(0, -42, -43, -44, -45, -46),
                     minor_breaks = seq(-2,-42,-2)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 10, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size)#,
        #plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
        ) +
  annotate(geom="text", label="SOC debt", x=factor(1995), y=-20, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -24, arrow=arrow(end="both", type="closed", length=unit(0.1, "inches")))

@@

grid <- plot_grid(SOCdensity,SOCincrease, SOCshare, SOCemis,  ncol=2, labels=c("(a)","(b)", "(c)", "(d)"),
                  label_fontface = "plain", label_size = 10)
grid
ggsave(paste0(outputdir,"/4panelfigure.png"), plot=grid, width = 20, height = 14, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCshare.png"),    plot=SOCshare,    width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCincrease.png"), plot=SOCincrease, width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCdensity.png"),  plot=SOCdensity,  width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCemis.png"),     plot=SOCemis,     width = 10, height = 7, dpi = 300, units = "cm")

### 2021-04-01 ResultNotebooks/results_SOCscenario.Rmd
add revision point by point replies

---
title: "Global SOC scenarios"
output:
  md_document:
    variant: markdown_github
  html_document:  
---

@@

rev         <- "rev16"
scenarios   <- c("histManagement","constManagement-1975", "constTillage-mixedtill", "constResidues-1975", "constManure-1975",
                  "constManagement2-1975", "constResrate-1975", "constYield-1975",
                 "Initial-natveg", "Initial-natveg_constManagement-1975", "Initial-natveg_constManagement2-1975", 
                 "LitterPNV-PerennialGrasses", "LitterPNV-AASS", "LitterPNV-BRCF", 
                 "LitterPNV-MTCF", "LitterPNV-BLEAF",  "LitterPNV-TREF")

# filesNeeded  <- c("SoilCarbon.rds","Landuse.rds")
# setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
# 
# untar(paste0(getConfig("outputfolder"),"/", rev, "histManagement_h12_carbonbudget.tgz"),
#       exdir="Data/histManagement", extras="--keep-newer-files ")
# 
# for(item in scenarios){
#    untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
#    files=filesNeeded, exdir=paste0("Data/", item), extras="--keep-newer-files ")
# }

@@

for(scen in scenarios){
  SoilCarbon <- read.magpie(paste0("Data/", scen, "/SoilCarbon.rds"))
  Landuse    <- read.magpie(paste0("Data/", scen, "/Landuse.rds"))
  SoilCarbon[,,"naturalstate.crop"] <- SoilCarbon[,,"naturalstate.natveg"]
  SOCStock        <- toolConditionalReplace(dimSums(dimSums(SoilCarbon[,,"state",pmatch=TRUE], dim=3.3)* Landuse, dim=3.2), "is.nan()",0)
  glo_SOCStock    <- mbind(glo_SOCStock, add_dimension(dimSums(SOCStock, dim=1), 
                                                       dim=3.1, nm=scen, add="scenario")) 
}

@@

limits <- c(-30,-21)
breaks <- c(-22, -24,- 26, -28, -30)

@@

limits <- c(-30,-10)
breaks <- c(-10, -15,- 20, -25, -30)

@@

limits <- c(-30,-18)
breaks <- c(-18, -22, -26, -30)

>>>>

---
title: "Global SOC scenarios"
output:
  md_document:
    variant: markdown_github
  html_document:  
    pdf_document: default
---

@@

rev         <- "rev19"
scenarios   <- c("histManagement","constManagement-1975", "constTillage-mixedtill", "constResidues-1975", "constManure-1975",
                  "constManagement2-1975", "constResrate-1975", "constYield-1975",
                 "Initial-natveg", "Initial-natveg_constManagement-1975", "Initial-natveg_constManagement2-1975", 
                 "LitterPNV-PerennialGrasses", "LitterPNV-AASS", "LitterPNV-BRCF", 
                 "LitterPNV-MTCF", "LitterPNV-BLEAF",  "LitterPNV-TREF")

filesNeeded  <- c("SoilCarbon.rds","Landuse.rds")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")

untar(paste0(getConfig("outputfolder"),"/", rev, "histManagement_h12_carbonbudget.tgz"),
      exdir=paste0("Data/",rev,"histManagement"), extras="--keep-newer-files ")

for(item in scenarios){
   untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
   files=filesNeeded, exdir=paste0("Data/", rev, item), extras="--keep-newer-files ")
}

@@

for(scen in scenarios){
  SoilCarbon <- read.magpie(paste0("Data/", rev, scen, "/SoilCarbon.rds"))
  Landuse    <- read.magpie(paste0("Data/", rev, scen, "/Landuse.rds"))
  SoilCarbon[,,"naturalstate.crop"] <- SoilCarbon[,,"naturalstate.natveg"]
  SOCStock        <- toolConditionalReplace(dimSums(dimSums(SoilCarbon[,,"state",pmatch=TRUE], dim=3.3)* Landuse, dim=3.2), "is.nan()",0)
  glo_SOCStock    <- mbind(glo_SOCStock, add_dimension(dimSums(SOCStock, dim=1), 
                                                       dim=3.1, nm=scen, add="scenario")) 
}

@@

limits <- c(-48,-42)
breaks <- c(-42, -44,- 46, -48)

@@

limits <- c(-50,-20)
breaks <- c(-20, -30,- 40, -50)

@@

limits <- c(-48,-40)
breaks <- c(-40, -42, -44, -46, -48)

### 2021-04-01 ResultNotebooks/results_SOCtable.Rmd
add revision point by point replies

rev       <- "rev16"
outputdir <- "Output/"

@@

SoilCarbon <- read.magpie(paste0("Data/histManagement/SoilCarbon.rds"))
Landuse    <- read.magpie(paste0("Data/histManagement/Landuse.rds"))

@@

MShare_ipcc <- LShare_ipcc <-  HShare_ipcc <- new.magpie("GLO",NULL,outer(c("IPCC2006","IPCC2019"),
                                                                          getNames(climateIPCC), paste, sep="."))

>>>>

scenarios <- c("rev19histManagement","rev18histManagement_ResAllom_2021_02_01")
outputdir <- "Output/"

@@

SoilCarbon <- read.magpie(paste0("Data/",scenarios[2],"/SoilCarbon.rds"))
Landuse    <- read.magpie(paste0("Data/",scenarios[2],"/Landuse.rds"))
```

@@

MShare_ipcc <- LShare_ipcc <-  HShare_ipcc <- new.magpie("GLO",NULL,outer(c("IPCC2006","IPCC2019"),
                                                                          getNames(climateIPCCr), paste, sep="."))
